Quantum Pseudo-Telepathy

### 2023-06-07 paper/main.tex
Summary quantum strat

As seen in Section~\ref{sec:classic-sol}, the \emph{magic} square is
called this way because, under classical assumptions, there is no such
a square: it is impossible to construct a \(3 \times 3\) matrix filled
with \(\pm 1\)'s, with the constraints that the product of every row
is \(+1\) and the product of every column is \(-1\). We can, however,
construct a ``quantum magic'' square. Figure~\ref{fig:quantum} shows
the \(3 \times 3\) grid that Alice and Bob can use to win the Magic
Square game systematically.  Notice that the eigenvalues of the
observables at each cell are \(\pm 1\). Furthermore, the product of
every row is \(+I\) and the product of every column is \(-I\).

>>>>

As seen in Section~\ref{sec:classic-sol}, the \emph{magic} square is
called this way because, under classical assumptions, there is no such
a square: it is impossible to construct a \(3 \times 3\) matrix filled
with \(\pm 1\)'s, with the constraints that the product of every row
is \(+1\) and the product of every column is \(-1\). We can, however,
construct a ``quantum magic'' square. Figure~\ref{fig:quantum} shows
the \(3 \times 3\) grid that Alice and Bob can use to win the Magic
Square game systematically.  Notice that the eigenvalues of the
observables at each cell are \(\pm 1\). Furthermore, the product of
every row is \(+I\) and the product of every column is \(-I\).  The
quantum strategy works as follows: Alice measures all the observables
from the \(i\)-th row of the predefined matrix. She fills each cell
with the result of each measurement. Similarly, Bob measures all the
observables in the \(j\)-th column that was assigned to him, and fills
each cell of his column with the outcomes of each
measurement. Example~\ref{ex:quantum-sol} depicts a round of the game.
